# Combining Territory Boundaries and Variables {background-color="#A1D6F4"}

## Overlap {background-color="#A1D6F4"}

- Mask the raster with the shapes and summarize the data that fall within each shape

- Amount of data depends on the size of the territory
- Small territories have less data than large ones

``` {r Masking example}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"
for (i in 1:nrow(zip_manhattan_nlcd_crs)) {
#for (i in 1:25) {
  if(i == 1) {
    all_data <- NULL
  } 

  zip <- zip_manhattan_nlcd_crs[i,]
  zip_code <- zip$ZCTA5CE20[1]
  
  cr <- crop(nlcd, extent(zip)) # Cropping first makes this faster
  mr <- mask(cr, zip)

  all_data[[i]] <- data.frame(cbind(ZCTA5CE20 = zip_code, freq(mr, bylayer = FALSE)))
}

masked_freq <- bind_rows(all_data) %>%
  mutate(count = as.numeric(count)) %>%
  rename(land_cover = value) %>%
  arrange(ZCTA5CE20, land_cover)

# Example
selected_zip <- "10034"
zip <- filter(zip_manhattan_nlcd_crs, ZCTA5CE20 == selected_zip)

cr <- crop(nlcd, extent(zip)) # Cropping first makes this faster
mr <- mask(cr, zip)

plot(mr)
plot(zip, add = TRUE, col = NA, title = selected_zip)
```
Then compute whatever static you want to try: min, median, average, max, predominant

## Masked Output Table {background-color="#A1D6F4"}

```{r Masked Output Table}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

datatable(masked_freq, rownames = FALSE, options = list(pagelength = 8))
```

## Masked Predominant Land Cover {background-color="#A1D6F4"}

```{r Masked Predominant Land Cover}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Predominant land cover
masked_predominant <- masked_freq %>%
  group_by(ZCTA5CE20) %>%
  arrange(ZCTA5CE20, desc(count)) %>%
  top_n(1)

datatable(masked_predominant, rownames = FALSE, options = list(pagelength = 8))
```

## Masked Pecent Land Cover {background-color="#A1D6F4"}

```{r Masked Percent Land Cover}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Percent of ZIP for each land cover
masked_percent <- masked_freq %>%
  group_by(ZCTA5CE20) %>%
  mutate(percent = count / sum(count)) %>%
  arrange(ZCTA5CE20, land_cover)

datatable(masked_percent, rownames = FALSE, options = list(pagelength = 8)) %>%
  formatPercentage('percent', digits = 1)
```

## Buffering {background-color="#A1D6F4"}

- Draw a square or circular buffer around each centroid
- More consistent number of data elements
- May fall short or go beyond the edges of the shape
- Edges of the data set become problematic
- This example uses circles

## Buffering Example {background-color="#A1D6F4"}

```{r Buffering example}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Create buffers
zip_buffers <- st_buffer(centroids, dist = 1000)  # 1 km buffer

# Loop through ZIPs
for (i in 1:nrow(zip_buffers)) {
#for (i in 1:25) {
  if(i == 1) {
    all_data <- NULL
  } 

  zip <- zip_buffers[i,]
  zip_code <- zip$ZCTA5CE20[1]
  
  # Crop and mask
  cr <- crop(nlcd, extent(zip)) # Cropping first makes this faster
  mr <- mask(cr, zip)

  # Calculate frequencies
  all_data[[i]] <- data.frame(cbind(ZCTA5CE20 = zip_code, freq(mr, bylayer = FALSE)))
}

# Build the complete data set
buffered_freq <- bind_rows(all_data) %>%
  mutate(count = as.numeric(count)) %>%
  rename(land_cover = value) %>%
  arrange(ZCTA5CE20, land_cover)

# Example

selected_zip <- "10034"
zip <- filter(zip_buffers, ZCTA5CE20 == selected_zip)

cr <- crop(nlcd, extent(zip)) # Cropping first makes this faster
mr <- mask(cr, zip)

plot(mr)
plot(filter(zip_manhattan_nlcd_crs, ZCTA5CE20 == selected_zip), col = NA,  add = TRUE, title = selected_zip)
```

## Buffered Output Table {background-color="#A1D6F4"}

```{r Buffered Table}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

datatable(buffered_freq, rownames = FALSE, options = list(pagelength = 8))
```

## Buffered Predominant Land Cover {background-color="#A1D6F4"}

```{r Buffered Predominant Land Cover}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Predominant land cover
buffered_predominant <- buffered_freq %>%
  group_by(ZCTA5CE20) %>%
  arrange(ZCTA5CE20, desc(count)) %>%
  top_n(1)

datatable(buffered_predominant, rownames = FALSE, options = list(pagelength = 8))
```

## Buffered Percent Land Cover {background-color="#A1D6F4"}

```{r Buffered Percent Land Cover}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Percent of ZIP for each land cover
buffered_percent <- buffered_freq %>%
  group_by(ZCTA5CE20) %>%
  mutate(percent = count / sum(count)) %>%
  arrange(ZCTA5CE20, land_cover)

datatable(buffered_percent, rownames = FALSE, options = list(pagelength = 8)) %>%
  formatPercentage('percent', digits = 1)
```

## Masked vs. Buffered {background-color="#A1D6F4"}

```{r Buffered vs. Percent}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# full_join data sets
masked_vs_buffered_percent <- masked_percent %>%
  full_join(buffered_percent, by = c("ZCTA5CE20", "land_cover"), suffix = c(".mask", ".buff"))

datatable(masked_vs_buffered_percent, rownames = FALSE, options = list(pagelength = 8)) %>%
  formatPercentage('percent.mask', digits = 1) %>%
  formatPercentage('percent.buff', digits = 1)
```

## Masked vs. Buffered - NAs {background-color="#A1D6F4"}

```{r Buffered vs. Percent - NAs}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Filter to nulls
masked_vs_buffered_percent_null <- masked_vs_buffered_percent %>%
  filter(is.na(count.mask) | is.na(count.buff))

datatable(masked_vs_buffered_percent_null, rownames = FALSE, options = list(pagelength = 8)) %>%
  formatPercentage('percent.mask', digits = 1) %>%
  formatPercentage('percent.buff', digits = 1)
```
