## Buffering {background-color="#A1D6F4"}

- Draw a square or circular buffer around each centroid
- More consistent number of data elements
- May fall short or go beyond the edges of the shape
- Edges of the data set become problematic
- This example uses circles

## Buffering Example {background-color="#A1D6F4"}

```{r Buffering example}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Create buffers
buffers <- st_buffer(centroids, dist = 1000)  # 1 km buffer

# Loop through ZIPs
for (i in 1:nrow(buffers)) {
#for (i in 1:1) {
  if(i == 1) {
    all_data <- NULL
  } 

  selected_buffer <- buffers[i,]
  selected_GEOID <- buffers$GEOID[i]
  
  # Crop and mask
  cropped_raster <- crop(nlcd, ext(selected_buffer)) # Cropping first makes this faster
  masked_raster <- mask(cropped_raster, selected_buffer)

  # Calculate frequencies
  all_data[[i]] <- data.frame(cbind(GEOID = selected_GEOID, freq(masked_raster, bylayer = FALSE)))
}

# Build the complete data set
buffered_freq <- bind_rows(all_data) %>%
  mutate(count = as.numeric(count)) %>%
  rename(land_cover = value) %>%
  arrange(GEOID, land_cover)

# Example

selected_geoid <- "36061013100"
selected_buffer <- filter(buffers, GEOID == selected_geoid)

cropped_raster <- crop(nlcd, ext(selected_buffer)) # Cropping first makes this faster
masked_raster <- mask(cropped_raster, selected_buffer)

plot(cropped_raster)
plot(selected_buffer, col = NA,  add = TRUE, title = selected_geoid)
```

## Buffered Output Table {background-color="#A1D6F4"}

```{r Buffered Table}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

datatable(buffered_freq, rownames = FALSE)
```

## Buffered Predominant Land Cover {background-color="#A1D6F4"}

```{r Buffered Predominant Land Cover}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Predominant land cover
buffered_predominant <- buffered_freq %>%
  group_by(GEOID) %>%
  arrange(GEOID, desc(count)) %>%
  top_n(1)

datatable(buffered_predominant, rownames = FALSE)
```

## Buffered Percent Land Cover {background-color="#A1D6F4"}

```{r Buffered Percent Land Cover}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Percent of ZIP for each land cover
buffered_percent <- buffered_freq %>%
  group_by(GEOID) %>%
  mutate(percent = count / sum(count)) %>%
  arrange(GEOID, land_cover)

datatable(buffered_percent, rownames = FALSE) %>%
  formatPercentage('percent', digits = 1)
```