## Overlap {background-color="#A1D6F4"}

- Mask the raster with the shapes and summarize the data that fall within each shape

- Amount of data depends on the size of the territory
- Small territories have less data than large ones

``` {r Masking example}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Example
selected_shape <- "36061013100" # Sheraton New York Times Square Hotel Census Tract
tract <- filter(new_york_county_tracts_nlcd_crs, GEOID == selected_shape)

cropped_raster <- crop(nlcd, ext(tract)) # Cropping first makes this faster
masked_raster <- mask(cropped_raster, tract)

plot(masked_raster)
plot(tract, add = TRUE, col = NA, title = selected_shape)
```
Then compute whatever static you want to try: min, median, average, max, predominant

## Masked Output Table {background-color="#A1D6F4"}

```{r Masked Output Table}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

for (i in 1:nrow(new_york_county_tracts_nlcd_crs)) {
  if(i == 1) {
    all_data <- NULL
  } 

  shape <- new_york_county_tracts_nlcd_crs[i,]
  GEOID <- new_york_county_tracts_nlcd_crs$GEOID[i]
  
  cropped_raster <- crop(nlcd, ext(shape)) # Cropping first makes this faster
  masked_raster <- mask(cropped_raster, shape)

  all_data[[i]] <- data.frame(cbind(GEOID = GEOID, freq(masked_raster, bylayer = FALSE)))
}

masked_freq <- bind_rows(all_data) %>%
  mutate(count = as.numeric(count)) %>%
  rename(land_cover = value) %>%
  arrange(GEOID, land_cover)


datatable(masked_freq, rownames = FALSE)
```

## Masked Pecent Land Cover {background-color="#A1D6F4"}

```{r Masked Percent Land Cover}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Percent of ZIP for each land cover
masked_percent <- masked_freq %>%
  group_by(GEOID) %>%
  mutate(percent = count / sum(count)) %>%
  arrange(GEOID, land_cover)

datatable(masked_percent, rownames = FALSE) %>%
  formatPercentage('percent', digits = 1)
```

::: {.notes}
Would probably transpose this so the different land covers are columns
Might set indictor variables with thresholds, like this land cover exists or it's more than x% this land cover
:::

## Masked Predominant Land Cover {background-color="#A1D6F4"}

```{r Masked Predominant Land Cover}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Predominant land cover
masked_predominant <- masked_freq %>%
  group_by(GEOID) %>%
  arrange(GEOID, desc(count)) %>%
  top_n(1) # Grabs the most common / predominant cover

datatable(masked_predominant, rownames = FALSE)
```

:::{.notes}

Hotel:
State: 36
County: 061
Tract: 36061013100
Block: 360610131002001
:::