## Overlap

- Mask the raster with the shapes and summarize the data that fall within each shape
  - Example statistics: min, median, average, max, predominant
- Amount of data depends on the size of the territory
- Small territories have less data than large ones

``` {r Masking example}
#| code-summary: "Census Tract / NLCD Overlap Mask"
#| code-fold: true
#| code-line-numbers: "|1-3|5-7|9-11"

# Sheraton New York Times Square Hotel Census Tract
selected_geoid <- "36061013100"
tract <- filter(new_york_county_tracts_nlcd_crs, GEOID == selected_geoid)

# Cropping then masking is faster
cropped_raster <- crop(nlcd, ext(tract))
masked_raster <- mask(cropped_raster, tract)

# Plot them on top of each other
plot(masked_raster)
plot(tract, add = TRUE, col = NA, title = selected_geoid)
```

## Masked Output Table

```{r Masked Output Table}
#| code-summary: "Census Tract / NLCD Overlap Mask - Loop"
#| code-line-numbers: "|1-9,12-14|10-11|16-21"

# Loop through all Census Tracts
for (i in 1:nrow(new_york_county_tracts_nlcd_crs)) {
  if(i == 1) {
    all_data <- NULL
  } 

  shape <- new_york_county_tracts_nlcd_crs[i,]
  GEOID <- new_york_county_tracts_nlcd_crs$GEOID[i]
  
  cropped_raster <- crop(nlcd, ext(shape)) # Cropping first makes this faster
  masked_raster <- mask(cropped_raster, shape)

  all_data[[i]] <- data.frame(cbind(GEOID = GEOID, freq(masked_raster, bylayer = FALSE)))
}

# Build data table
masked_freq <- bind_rows(all_data) %>%
  mutate(count = as.numeric(count)) %>%
  rename(land_cover = value) %>%
  arrange(GEOID, land_cover)
```

::: {.notes}
Essentially we're computing this for each one

I'm doing a simple loop here for the example

If you're really building these, then more of the work goes into setting it up so the calculation can be run in parallel and handle errors

Hotel:
State: 36
County: 061
Tract: 36061013100
Block: 360610131002001
:::

## Masked Frequency Data Table

```{r Masked Census Tract / NLCD Overlap Frequency Table}
#| code-summary: "Show code"
#| code-fold: true

# Display table on slide
datatable(masked_freq, rownames = FALSE)
```

## Masked Pecent Land Cover

```{r Masked Percent Land Cover}
#| code-summary: "Census Tract / NLCD Overlap Mask - Percent Land Cover"
#| code-line-numbers: "|1-5|3-4"

# Percent of each Land Cover in Each Tract
masked_percent <- masked_freq %>%
  group_by(GEOID) %>%
  mutate(percent = count / sum(count)) %>%
  arrange(GEOID, land_cover)

# Display table on slide
datatable(masked_percent, rownames = FALSE) %>%
  formatPercentage('percent', digits = 1)
```

::: {.notes}
Would probably transpose this so the different land covers are columns
Might set indictor variables with thresholds, like this land cover exists or it's more than x% this land cover
:::

## Masked Predominant Land Cover

```{r Masked Predominant Land Cover}
#| code-summary: "Census Tract / NLCD Overlap Mask - Predominant Land Cover"
#| code-line-numbers: "|5"

# Predominant Land Cover in Each Tract
masked_predominant <- masked_freq %>%
  group_by(GEOID) %>%
  arrange(GEOID, desc(count)) %>%
  top_n(1) # Grabs the most common / predominant cover

# Display table on slide
datatable(masked_predominant, rownames = FALSE)
```

:::{.notes}


:::