## Tech Stack

- R
- RStudio - IDE from the company Posit (formerly named RStudio)
- Mac - You'll need to swap "/" to "\\" to render on PC
- Quarto - Presentation + code together
- GitHub - Source code control
- GitHub Pages - Publishing the rendered presentation online (automatically!)


::: {.notes}
Obviously given the title of the presentation, we're using R.

There's nothing magical about R here, the concepts apply to languages like Python and platforms like QGIS, ArcGIS, Mapbox, CARTO, etc.

:::

## Tech Stack - R Libraries

```{r import_libraries}
#| code-summary: "Import libraries"
#| code-line-numbers: "|1-5|7-11|12-14"

# Geospatial-specific
library(sf) # For working with vector geospatial data. Replaced rgdal and rgeos
library(terra) # For working with raster geospatial data. Replaced raster
terraOptions(progress = 0) # Turn off progress bars so they don't end up on slides
library(leaflet) # For interactive maps

# Support
library(curl) # For downloading files
library(readr) # For reading CSVs
library(dplyr) # For manipulating data

# Interface to JavaScript library DataTables
library(DT)
options(DT.options = list(pageLength = 8))
```

::: {.notes}
Here are the libraries we'll use for this presentation. There are three main geospatial ones: sf, terra, and leaflet

I also reference curl, readr, and dplyr for downloading and data manipulation, and DT for making interactive data tables.
:::

## Tech Stack - Download Helper Function

```{r Download Helper}
#| code-summary: "Download Helper"
#| code-line-numbers: "|6-11|13-18"

download_data <- function(url, relative_dir) {
  
  # URL
  filename <- basename(url)
  
  # Download to Data In
  dest_in <- paste("./data_in", relative_dir, filename, sep = "/")
  if(!file.exists(dest_in)) {
    dir.create(dirname(dest_in), recursive = TRUE, showWarnings = FALSE)
    curl_download(url, dest_in)
  }
  
  # Extract to Data Mid
  dest_mid <- paste("./data_mid", relative_dir, filename, sep = "/")
  if(!file.exists(dest_mid)) {
    dir.create(dirname(dest_mid), recursive = TRUE, showWarnings = FALSE)
    unzip(dest_in, exdir = dirname(dest_mid))
  }
}
```

::: {.notes}
I use this function create and download files

I'm not going to go through it since the focus is on geospatial data

That said, I tend to structure data sets in my projects into an in, mid/intermediary
:::