## Tech Stack

- R
- Integrated Development Environments (IDEs)
  - RStudio - IDE from the company Posit (formerly named RStudio)
  - Positron - Visual Studio Code-based IDE from Posit
- Quarto - Presentation + code together
- GitHub - Source code control
- GitHub Pages - Publishing the rendered presentation online (automatically!)

::: {.notes}
Obviously given the title of the presentation, we're using R.

I used a mix of RStudio, and Positron for creating the presentation. Positron is the new VS Code-based IDE from Posit, which is the company formerly know as RStudio

There's nothing magical about R here, the concepts apply to languages like Python and platforms like QGIS, ArcGIS, Mapbox, CARTO, etc.
:::

## Tech Stack - R Libraries

```{r import_libraries}
#| code-line-numbers: "1-5|7-11|12-14"
#| echo: true
#| code-fold: false
#| code-summary: "Import libraries"

# Geospatial-specific
library(sf) # For working with vector geospatial data. Replaced rgdal and rgeos
library(terra) # For working with raster geospatial data. Replaced raster
terraOptions(progress = 0) # Turn off progress bars so they don't end up on slides
library(leaflet) # For interactive maps

# Support
library(curl) # For downloading files
library(readr) # For reading CSVs
library(dplyr) # For manipulating data

# Interface to JavaScript library DataTables
library(DT)
options(DT.options = list(pageLength = 8, ordering = FALSE))
```

::: {.notes}
Here are the libraries we'll use for this presentation. There are three main geospatial ones: sf, terra, and leaflet

I also reference curl, readr, and dplyr for downlaoding and data manipulation, and DT for making interactive data tables.
:::

## Tech Stack - Download Helper Function

```{r Download Helper}
#| echo: true
#| code-fold: false
#| code-summary: "Download Helper"

download_data <- function(url, relative_dir) {
  
  filename <- basename(url)
  dest_in <- paste("./data_in", relative_dir, filename, sep = "/")
  dest_mid <- paste("./data_mid", relative_dir, filename, sep = "/")
  
  if(!file.exists(dest_in)) {
    dir.create(dirname(dest_in), recursive = TRUE, showWarnings = FALSE)
    curl_download(url, dest_in)
    
    dir.create(dirname(dest_mid), recursive = TRUE, showWarnings = FALSE)
    unzip(dest_in, exdir = dirname(dest_mid))
  }
  
  dest_mid
}
```

::: {.notes}
I use this function create and download files

I'm not going to go through it since the focus is on geospatial data

You can review it at your leisure
:::