## Tech Stack

- R
- Integrated Development Environments (IDEs)
  - RStudio - IDE from the company Posit (formerly named RStudio)
  - Positron - Visual Studio Code-based IDE from Posit
- Quarto - Presentation + code together
- GitHub - Source code control
- GitHub Pages - Publishing the rendered presentation online (automatically!)

## Tech Stack - R Libraries

```{r Import libraries}
#| echo: true
#| code-fold: false
#| code-summary: "Import libraries"

# Geospatial-specific
library(sf) # For working with vector geospatial data. Replaced rgdal and rgeos
library(terra) # For working with raster geospatial data. Replaced raster
terraOptions(progress = 0) # Turn off progress bars so they don't end up on slides
library(leaflet) # For interactive maps

# Others

library(curl) # For downloading files
library(readr) # For reading CSVs
library(dplyr) # For manipulating data

# Interface to JavaScript library DataTables
library(DT)
options(DT.options = list(pageLength = 8, ordering = FALSE))
```

## Tech Stack - Download Helper Function

Function to help download files if they don't exist

```{r Download Helper}
#| echo: true
#| code-fold: false
#| code-summary: "Download Helper"

download_data <- function(url, relative_dir) {
  
  filename <- basename(url)
  dest_in <- paste("./data_in", relative_dir, filename, sep = "/")
  dest_mid <- paste("./data_mid", relative_dir, filename, sep = "/")
  
  if(!file.exists(dest_in)) {
    dir.create(dirname(dest_in), recursive = TRUE, showWarnings = FALSE)
    curl_download(url, dest_in)
    
    dir.create(dirname(dest_mid), recursive = TRUE, showWarnings = FALSE)
    unzip(dest_in, exdir = dirname(dest_mid))
  }
  
  dest_mid
}
```
