## Counties and County Equivalents

```{r Download Countrywide Counties ()}
#| echo: true
#| code-fold: true
#| code-summary: "Download and read in County Shapefile"
#| results: "hide"

url <- "https://www2.census.gov/geo/tiger/TIGER2025/COUNTY/tl_2025_us_county.zip"
dest_in <- "./data_in/census/TIGER2025/COUNTY/tl_2025_us_county.zip"
dest_mid <- "./data_mid/census/TIGER2025/COUNTY/tl_2025_us_county/tl_2025_us_county.zip"

if(!file.exists(dest_in)) {
  dir.create(dirname(dest_in), recursive = TRUE, showWarnings = FALSE)
  curl_download(url, dest_in)
  
  dir.create(dirname(dest_mid), recursive = TRUE, showWarnings = FALSE)
  unzip(dest_in, exdir = dirname(dest_mid))
}

# Read Census State Shapefile
census_county  <- read_sf("./data_mid/census/TIGER2025/COUNTY/tl_2025_us_county/tl_2025_us_county.shp")

```

```{r New York Counties}
#| echo: true
#| code-fold: true
#| code-summary: "Leaflet County Map"

census_county %>%
  filter(STATEFP == "36") %>%
  leaflet() %>%
  addTiles() %>% # Added OpenStreetMap Basemap
  addPolygons(weight = 0.5, opacity = 1.0)
```

::: {.notes}

County and county equivalents

The wikipedia page has some good discussion of "County Equivalents" https://en.wikipedia.org/wiki/List_of_United_States_counties_and_county_equivalents

Some companies use county (and equivalent) for territory

From three in Delaware to 254 in Texas.

Radically different sizes. Some of the unorganized territories in Alaska are huge

Zoom in on Manhattan County. Note Cobble Hill across the river
:::