## States

```{r Read Census Bureau Shapefile & Display Data}
#| code-summary: "Read Census Bureau Shapefile & Display Data"
#| code-line-numbers: "1-4|6-7|9-10"

# Download data using our helper function
download_data(
  url = "https://www2.census.gov/geo/tiger/TIGER2025/STATE/tl_2025_us_state.zip",
  relative_dir = "census/TIGER2025/STATE")

# Read Shapefile
census_state  <- read_sf("./data_mid/census/TIGER2025/STATE/tl_2025_us_state.shp")

# Print data table
census_state %>% arrange(STATEFP) %>% print(n = Inf)
```

::: {.notes}

* We'll use the read_sf function in the simple features package to read the shapefile
* We have two things available to us: a data table and the shapes. Let's look at the data table first

* The summary at the top lets us know the bounding box, or extent, of the shapes.
* Where it says "A tibble", it shows there are 56 of the 50 states + DC represented. The extras are the territories.
* The columns we care about are STATEFP, STUSPS, and NAME
* STATEFP is a handy code used throughout the Census data. If you look at rows 2 and 3, you'll see it skips from 02 to 04. The states are coded from 01 to 56, with placeholders to slot in territories alphabecially if they're converted to states. Note that on row 9, the Federal District, DC, is slotted in place with STATEFP = 11.

* geometry <MULTIPOLYGON [°]>

* This doesn't have the Census data, like population or household units attached. If you want to use those, you'll need to attach them

State: Since regulatory approval is by state, this is the least granular your territory can possibly be
:::

## New York Leaflet Plot

```{r Census State Leaflet Plot - NY}
#| code-summary: "Leaflet Plot - NY"
#| code-line-numbers: "1|2|3|4"

census_state %>%
  filter(STUSPS == "NY") %>%
  leaflet() %>%
  addPolygons(weight = 0.5, opacity = 1.0)
```

## New York Leaflet Plot With Basemap

```{r Census State Leaflet Plot With Basemap - NY}
#| code-summary: "Add Basemap"
#| code-line-numbers: "5"

census_state %>%
  filter(STUSPS == "NY") %>%
  leaflet() %>%
  addPolygons(weight = 0.5, opacity = 1.0) %>%
  addTiles() # Added OpenStreetMap Basemap
```
