## SSURGO

:::{.incremental} 

- Download **by county** from [Web Soil Survey](https://websoilsurvey.nrcs.usda.gov/app/WebSoilSurvey.aspx)
- Shapefile with an ID
- Separate text files contain the data
  - [Documentation](https://www.nrcs.usda.gov/resources/data-and-reports/soil-survey-geographic-database-ssurgo)
- Sample variables 
  - Drainage classification 
  - Available water storage (varying depths)
  - Bedrock Depth
  - Ponding Frequency
:::

::: {.notes }

SERFF: FAIG-134593537, MUOF-134283674, AMMH-134210246

:::

## SSURGO - Download Manhattan County Data

```{r Download Soil Survey Data, Set Names, & Data Types}
#| code-summary: "Download Soil Survey Data, Set Names, & Data Types"
#| echo: true

download_data(
  url = "https://websoilsurvey.sc.egov.usda.gov/DSD/Download/Cache/SSA/wss_SSA_NY061_soildb_US_2003_[2025-08-28].zip",
  relative_dir = "ssurgo")

muaggatt_names <- c(
  "musym",
  "muname",
  "mustatus",
  "slopegraddcp",
  "slopegradwta",
  "brockdepmin",
  "wtdepannmin",
  "wtdepaprjunmin",
  "flodfreqdcd",
  "flodfreqmax",
  "pondfreqprs",
  "aws025wta",
  "aws050wta",
  "aws0100wta",
  "aws0150wta",
  "drclassdcd",
  "drclasswettest",
  "hydgrpdcd",
  "iccdcd",
  "iccdcdpct",
  "niccdcd",
  "niccdcdpct",
  "engdwobdcd",
  "engdwbdcd",
  "engdwbll",
  "engdwbml",
  "engstafdcd",
  "engstafll",
  "engstafml",
  "engsldcd",
  "engsldcp",
  "englrsdcd",
  "engcmssdcd",
  "engcmssmp",
  "urbrecptdcd",
  "urbrecptwta",
  "forpehrtdcp",
  "hydclprs",
  "awmmfpwwta",
  "mukey")

muaggatt_types <- c("cclnnnnnccnnnnnccclnnncccccccccccccncnnc")
```

## SSURGO - Manhattan - Available Water Storage to 50 CM



```{r Manhattan SSURGO}
#| code-summary: "Read, join, & display SSURGO data"
#| code-line-numbers: "|1-5|7-9|11-12|14-16|17-19|20-24"

# Read muaggatt data file for New York County
muaggatt <- read_delim(
  "data_mid/ssurgo/NY061/tabular/muaggatt.txt", delim = "|",
  col_names = muaggatt_names,
  col_types = muaggatt_types)

# Read shapefile for New York, NY county
ssurgo <- read_sf("data_mid/ssurgo/NY061/spatial/soilmu_a_ny061.shp") %>%
  left_join(muaggatt, c ("MUKEY" = "mukey"))

# Define color palate - these are always annoying
aws_pal <- colorBin("Blues", ssurgo$aws050wta, 5, pretty = FALSE)

# Create available water storage plot plot
ssurgo %>%
  leaflet() %>%
  addPolygons(weight = 0.5,
              opacity = 1.0, fillOpacity = 1.0,
              fillColor = ~aws_pal(aws050wta)) %>%
  addLegend(
    pal = aws_pal,
    values = ~aws050wta,
    position = "bottomright",
  title = "Available Water Storage to a Depth of 50 CM")
```

:::{.notes }
"Available water storage or available water capacity (AWC) refers to the quantity of water that the soil is capable of storing for use by plants. The capacity for water storage is given in centimeters of water per centimeter of soil for each soil layer"
:::