## No. 2: Allstate

Allstate Vehicle and Property Insurance Company (37907)

ZIP Code-based territories

+-----------------------------------------------------------+
| [**Perils**]{style="display: block; text-align: center;"} |                                                 |
+------------+-------------------+-----------+--------------+
| Fire 1     | Water Weather     | Wind      | Theft        |
+------------+-------------------+-----------+--------------+
| Fire 2     | Water Non-weather | Hail      | Liability    |
+------------+-------------------+-----------+--------------+
| Brush Fire | Hurricane         | Lightning | Other        |
+------------+-------------------+-----------+--------------+

::: {.notes}
Their eSurance company in Nevada uses 0.05, 0.1, 0.2, 0.4 grid  SERFF ESUR-129867328 Page 920

:::

```{r Read in Allstate Factors & Join to ZCTA File}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Read in Allstate factor table
allstate_ny <- read_csv("./references_private/allstate_factors.csv",
                        col_names = c("zip",
                                      "fire1", "fire2", "brush_fire", "water_weather",
                                      "water_nonweather", "wind", "hail", "lightning",
                                      "theft", "liability", "hurricane", "other"),
                        skip = 1)

# Join factors to ZIP shapefile
zip_allstate_ny <- zcta %>%
  # Simplify the shape so the deck doesn't exceed the 100 MB limit of GitHub
  st_simplify(preserveTopology = TRUE, dTolerance = 50) %>%
  inner_join(allstate_ny, by = c("ZCTA5CE20" = "zip"))
```

## Allstate - Weather Water

```{r Allstate NY Weather Water}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Set up a color palette
pal <- colorBin(
  palette = c("#4575b4", "#91bfdb","#e0f3f8","#fee090","#fc8d59","#d73027"),
  domain = zip_allstate_ny$water_weather,
  bins = c(0.6, 0.8, 1.0, 1.20, 1.4, 1.6, 1.8),
  na.color = "transparent"
)

# Plot on top of Open Street Maps basemap
leaflet(zip_allstate_ny) %>%
  addTiles() %>%
  addPolygons(
    fillColor = ~pal(water_weather),
    color = "white",
    weight = 1.0,
    fillOpacity = 0.7) %>%
  addLegend(pal = pal, values = ~water_weather, title = "Weather Water")
```

## Allstate - Wind

```{r Allstate NY Wind}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"


# Set up a color palette
pal <- colorBin(
  palette = c("#4575b4", "#91bfdb","#e0f3f8","#fee090","#fc8d59","#d73027"),
  domain = zip_allstate_ny$wind,
  bins = c(0.6, 0.8, 1.0, 1.20, 1.4, 1.6, 1.8),
  na.color = "transparent"
)

# Plot on top of Open Street Maps basemap
leaflet(zip_allstate_ny) %>%
  addTiles() %>%
  addPolygons(
    fillColor = ~pal(wind),
    color = "white",
    weight = 1.0,
    fillOpacity = 0.7) %>%
  addLegend(pal = pal, values = ~wind, title = "Wind")
```



## Allstate - Theft

```{r Allstate NY Theft}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"


# Set up a color palette
pal <- colorBin(
  palette = c("#4575b4", "#91bfdb","#e0f3f8","#fee090","#fc8d59","#d73027"),
  domain = zip_allstate_ny$theft,
  bins = c(0.5, 0.75, 1.0, 1.25, 1.5, 1.75, 2.00),
  na.color = "transparent"
)

# Plot on top of Open Street Maps basemap
leaflet(zip_allstate_ny) %>%
  addTiles() %>%
  addPolygons(
    fillColor = ~pal(theft),
    color = "white",
    weight = 1.0,
    fillOpacity = 0.7) %>%
  addLegend(pal = pal, values = ~theft, title = "Hurricane Factor")
```


## Allstate - Hurricane

```{r Allstate NY hurricane factors}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Set up a color palette
pal <- colorBin(
  palette = c("#4575b4", "#91bfdb","#e0f3f8","#ffffbf","#fee090","#fc8d59","#d73027"),
  domain = zip_allstate_ny$hurricane,
  bins = c(0, 0.5, 1.5, 2.5, 4.0, 5.0, 6.0, 7.5, 10.0),
  na.color = "transparent"
)

# Plot on top of Open Street Maps basemap
leaflet(zip_allstate_ny) %>%
  addTiles() %>%
  addPolygons(
    fillColor = ~pal(hurricane),
    color = "white",
    weight = 1.0,
    fillOpacity = 0.7) %>%
  addLegend(pal = pal, values = ~hurricane, title = "Hurricane Factor")
```
