## State Farm Group (176)

State Farm Group (176)

State Farm Fire And Casualty Company (25143)

Ranked #1 in NY ($1.2B in 2024 Direct Written Premium)

- Granularity: "Location Rating" Grid
  - Decimal degrees to two decimal places
- 2 Perils:
    - Hurricane 
    - Non-Hurricane
- Source: 4,637 PDF pages of data

::: {.notes}
Extracted using Tabula
Excel get data from PDF also works well
:::

## State Farm Fire And Casualty Company (25143) - Non-Hurricane Factors

```{r New York State}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"

# Starts extracting the table from PDF
sf_ny <- read_csv("./references_private/state_farm_20200715.csv", col_names = c("GRID_ID", "HURR_FCTR", "NONHURR_FCTR"))  %>%
  mutate( # This parses the coordinate out of GRID_ID
    y =   0.01 * as.numeric(substr(GRID_ID, 1, 5)),
    x = - 0.01 * as.numeric(substr(GRID_ID, 6, 10)))

# Turn it into a raster
nonhurr_ny <- rast(sf_ny[, c("x", "y", "NONHURR_FCTR")], crs = crs('+proj=longlat +datum=WGS84'))

# Set up a color palette
pal <- colorBin(
  palette = c("#2c7bb6", "#abd9e9","#ffffbf","#fdae61","#d7191c"),
  domain = values(nonhurr_ny),
  bins = c(0.75, 1.0, 1.25, 1.5, 1.75),
  na.color = "transparent"
)

# Useful for seeing how frequent factors are
# Override digits since it rounds to integers by default
# freq(nonhurr_ny, digits = 3)
leaflet() %>%
  addTiles() %>%
  addRasterImage(nonhurr_ny, colors = pal, opacity = 0.5) %>%
  addLegend(pal = pal, values = values(nonhurr_ny), title = "Non-Hurricane Factor")
```

## State Farm Fire And Casualty Company (25143) - Hurricane Factors

```{r State Farm NY hurricane factors}
#| echo: true
#| code-fold: true
#| code-summary: "Show code"


# Turn it into a raster
hurr_ny <- rast(sf_ny[, c("x", "y", "HURR_FCTR")], crs = crs('+proj=longlat +datum=WGS84'))

# Set up a color palette
pal <- colorBin(
  palette = c("#2c7bb6", "#abd9e9","#ffffbf","#fdae61","#d7191c"),
  domain = values(hurr_ny),
  bins = c(0, 0.5, 1.5, 2.0, 2.5, 3.0),
  na.color = "transparent"
)

leaflet() %>%
  addTiles() %>%
  addRasterImage(hurr_ny, colors = pal, opacity = 0.5) %>%
  addLegend(pal = pal, values = values(hurr_ny), title = "Hurricane Factor")
```
